### 2019-07-18 manuscript/methods.tex
- Itay's comments #21-33, only. Not done: #1-20, #34-35.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. Character state abbreviations: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
(A) The five categories and the number of species in our data for each category.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC ($CP$).
(B) Category groupings into states for each model type.
For example, there are 70 species that are SC with unknown ploidy.
In the ploidy only models (M1- M10) these are coded as $D$ and $P$ (uncertain/consistent with either state), in the breeding system only models (M11-M15) they are coded as $C$, and in the ploidy and breeding system models (M16-M29) they are coded as $CD$ and $CP$.
In the hidden state models, all species were coded as consistent with both $A$ and $B$.
Two species, \emph{Lycium californicum} and \emph{Solanum bulbocastanum}, are simultaneously $ID$ and $CP$, and by adding them the sample adds to the total of 651 taxa used for analyses.
}
\label{figure:stateclassifications}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used in the models.
(A) Each species retained on the phylogeny belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known. 
Number of species in each category is indicated; for example, 70 species are self-compatible with unknown ploidy.
Character state abbreviations are: $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, self-incompatible species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC ($CP$).
(B) Category groupings into states for each model class.
In the ploidy-only models (M1- M10), states are coded as $D$ \& $P$ when uncertain/consistent with either state; in the breeding system-only models (M11-M15) such states are coded as $C$; in the ploidy and breeding system models (M16-M29), they are coded as $CD$ \& $CP$.
In the hidden-trait models, all species could take on either of two `hidden' character states. %IM: #33 %B: NOT USING A/B because that confuses panel A and panel B designations unnecessarily. 
Two species, \emph{Lycium californicum} and \emph{Solanum bulbocastanum}, are simultaneously $ID$ and $CP$, and by adding them the sample adds to the total of 651 taxa used for analyses.
}
\label{figure:stateclassifications}
\end{figure}

### 2019-07-18 manuscript/results.tex
Fixed all todos and revised discussion issues
- Itay's comments #21-33, only. Not done: #1-20, #34-35.

When considering ploidy alone, we found a larger net diversification rate for diploids than for polyploids, in agreement with \citet{mayrose_2011, mayrose_2015}.
This result holds with (model M1, \cref{figure:netdivall}A) or without the diploidization parameter (M6, \cref{suppfigure:alldip}A).
Incorporating a hidden state in this model, however, reduces the clear separation in diversification rate estimates between diploids and polyploids (M4, \cref{figure:netdivall}B; M9, \cref{suppfigure:alldip}B).
Statistical model comparisons show a clear preference for models in which only a hidden state affects diversification or a hidden state as well as ploidy (M2 and M4; \cref{table:bayesfactors}).
Results are similar when diploidization is included (\cref{supptable:M6M10}).
Thus, the role of ploidy in net diversification is unclear, with rate differences perhaps better explained by another factor.

@@

When considering breeding system alone (M11, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included, the large net diversification rate difference persists for one hidden state but is diminished for the other (M14, \cref{figure:netdivall}D).
In the statistical model comparisons, the best two supported models include diversification differences due both to breeding system and to a hidden trait (M14 and M15, \cref{table:M11M15}).
Thus, breeding system seems to play a role in diversification differences, though a hidden factor does as well.

@@

When a hidden state is included, the separation in net diversification rate of ID \vs CD and CP persists within one hidden state but is reduced in the other (M19, \cref{figure:netdivall}F).
The same general pattern remains when diploidization is included (\cref{suppfigure:alldip}F).
Model comparisons clearly favor models that include ploidy, breeding system, and the hidden trait, against the character-independent model in which the focal traits do not influence diversification (\cref{supptable:M16M20}; \cref{supptable:M21M25} with diploidization). % add model numbers

@@

    \item Are diversification patterns only determined by hidden states and not the traits of interest?
    No, our focal traits are supported as having associations with diversification differences.
    In most cases, we find moderate to strong preference for models with the focal traits as well as hidden states, over models with only hidden states \cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).

    \item Are hidden states necessary to explain diversification rate heterogeneity?
    Yes, models with hidden states that influence diversification are strongly preferred over models containing only the focal traits (\cref{supptable:testaddhidden}).
    This means that there are potentially many sources of diversification shifts within the family.

@@

    \item Are conclusions robust to assumptions about hidden state transitions?
    Yes, we found that allowing different types of asymmetry in transitions within and between hidden states did not change our conclusions about net diversification differences.
    Hidden state models with asymmetric rates are, however, strongly preferred over models with equal rates between hidden states (\cref{supptable:asymmetry}), and they show stronger differences between some net diversification rates \cref{suppfigure:asymmetric}.

    \item Is there evidence for diploidization?
    Perhaps: when comparing models with diploidization against models without it, we found moderate evidence that models containing diploidization are preferred (\cref{supptable:testdiploidization}).
    We discuss later some further challenges in identifying diploidization.
    We further found that our main conclusions about net diversification differences are not dependent on whether diploidization in included (\cref{suppfigure:alldip}).

@@

The preceding conclusions, however, ignore the changes in numbers of lineages in each state due to speciation and extinction.
By analogy, envisioning the states as stepping stones, the extent to which each stone grows or shrinks over time affects the utility of each possible path.
Allowing for the different net diversification rates for each state (again using median rate estimates from M16), we find a qualitative difference in the relative pathway contributions.
The lower rate of net diversification in the $CD$ state, relative to $ID$, means that relatively fewer lineages are available to complete the second step of the two-step pathway, ending in $CP$.
Consequently, even over long timescales, we find that the two-step pathway contributes less to the formation of polyploids (\cref{figure:pathways}, right panels) when considering diversification as well as transitions.

%--------------------------------------------------
% \subsection{Model selection key questions}
% 
% \subsubsection{Are diversification patterns only determined by hidden states?}
% Whether the determination of the diversification is dependent on the focal traits and not only on the hidden state was done via the comparisons of character independent models against the focal traits w/o hidden states models (results shown in  \cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
% The general pattern is to moderate- to strongly prefer models with focal traits and asymmetric hidden states over the rest of the models with the exception of the ploidy only model where the character independent model (M2) seems to be equally preferred($K=0.5$) as the model with ploidy and asymmetric hidden rates (M4, \cref{table:bayesfactors}).
% 
% \subsubsection{Are hidden states necessary?}
% In the comparisons of simple diversification models of focal traits against models with hidden states we found that models with asymmetric hidden traits are strongly preferred over simpler models (summarized in table \cref{supptable:testaddhidden}).
% 
% \subsubsection{Is a second trait adding information to the diversification process?}
% As summarized in  \cref{table:lumped}, it is moderately preferred to add breeding system to ploidy only models (\cref{suppfigure:lumpedDP}).
% When adding ploidy information to breeding system models to create a three-state model, we found that there is no evidence that it is preferred (M28 vs. M16 \cref{suppfigure:lumpedIC}B and C). 
% However, it becomes moderately preferable in the presence of hidden states (M29 vs. M23  \cref{suppfigure:lumpedIC}E and C).
% 
% \subsubsection{Is there evidence for diploidization?}
% We considered models both with and without diploidization in order to explore its effects on the estimates of state-dependent diversification.
% For the models that only include diploid and polyploid states (M6-M10) the results are similar in terms of the effect of diversification (\cref{suppfigure:alldip}).
% When comparing models with diploidization against models without diploidization we found moderate evidence that models containing the parameter $\delta$ are preferred over models without diploidization (summarized in \cref{supptable:testdiploidization}).
% 
% \subsubsection{Do asymmetric rates in hidden states models affect the pattern of diversification?}
% When comparing different types of asymmetry across hidden states models we found that the asymmetry did not change the direction of effects in net diversification results . However, models with asymmetric hidden rates reduced the overlap amongst net diversification posterior distributions as shown in \cref{suppfigure:asymmetric}. Furthermore, hidden state models with asymmetric traits are strongly preferred over models with equal rates between hidden states (summarized in \cref{supptable:asymmetry}).
%--------------------------------------------------

>>>>

When considering ploidy alone, we found a larger net diversification rate for diploids than for polyploids, in agreement with \citet{mayrose_2011, mayrose_2015}.
This result holds with (model M1, \cref{figure:netdivall}A) or without the diploidization parameter (M6, \cref{suppfigure:alldip}A).
Incorporating a hidden state in this model, however, reduces the clear separation in diversification rate estimates between diploids and polyploids (M4, \cref{figure:netdivall}B; M9, \cref{suppfigure:alldip}B).
Statistical model comparisons show a clear preference for models in which only a hidden state affects diversification or a hidden state as well as ploidy (M2 and M4; \cref{table:bayesfactors}).
Results are similar when diploidization is included (\cref{supptable:M6M10}).
Thus, when other traits are ignored, the role of ploidy in net diversification is unclear, with marginal support for diploids having higher diversification rates, but rate differences perhaps better explained by another factor. %IM: #21

@@

When considering breeding system alone (M11, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included, the large net diversification rate difference persists for one hidden state but is diminished for the other (M14, \cref{figure:netdivall}D).
In the statistical model comparisons, the best two supported models include diversification differences due to both breeding system and to a hidden trait (M14 and M15, \cref{table:M11M15}). %IM: #22
Breeding system seems to play a role in diversification differences, though a hidden factor does as well.

@@

When a hidden state is included, the separation in net diversification rate of ID \vs CD and CP persists within one hidden state but is reduced in the other (M19, \cref{figure:netdivall}F).
The same general pattern remains when diploidization is included (\cref{suppfigure:alldip}F).
Model comparisons clearly favor models that include ploidy, breeding system, and the hidden trait, against the character-independent model in which the focal traits do not influence diversification (\cref{supptable:M16M20}; \cref{supptable:M21M25} with diploidization).

@@

    \item Are diversification patterns only determined by hidden states and not the traits of interest?
    No, our focal traits are supported as having associations with diversification differences.
    In most cases, we find moderate to strong preference for models with the focal traits as well as hidden states, over models with only hidden states (\cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}). %IM: #23

    \item Are hidden states necessary to explain diversification rate heterogeneity?
    Yes, models with hidden states that influence diversification are strongly preferred over models containing only the focal traits (\cref{supptable:testaddhidden}).
    This means that there are potentially many factors underlying diversification shifts within the family. %IM: #24

@@

    \item Are conclusions robust to assumptions about hidden state transitions?
    Yes, we found that allowing different types of asymmetry in transitions within and between hidden states did not change our conclusions about net diversification differences.
    Hidden state models with asymmetric rates are, however, strongly preferred over models with equal rates between hidden states (\cref{supptable:asymmetry}), and they show stronger differences between some net diversification rates (\cref{suppfigure:asymmetric}).

    \item Is there evidence for diploidization?
    Perhaps: when comparing models with diploidization against models without it, we found moderate evidence that models containing diploidization are preferred (\cref{supptable:testdiploidization}).
    We discuss later some further challenges in identifying diploidization.
    We further found that our main conclusions about net diversification differences are not dependent on whether diploidization is included (\cref{suppfigure:alldip}). %IM: #26

@@

The preceding conclusions, however, ignore the changes in numbers of lineages in each state due to speciation and extinction.
By analogy, envisioning the states as stepping stones, the extent to which each stone grows or shrinks over time affects the utility of each possible path.
Allowing different net diversification rates for each state (again using median rate estimates from M16), we find a qualitative difference in the relative pathway contributions. %IM: #27
The lower rate of net diversification in the $CD$ state, relative to $ID$, means that relatively fewer lineages are available to complete the second step of the two-step pathway, ending in $CP$.
Consequently, even over long timescales, we find that the two-step pathway contributes less to the formation of polyploids (\cref{figure:pathways}, right panels) when considering diversification as well as transitions.

### 2019-07-18 manuscript/tables.tex
- Itay's comments #21-33, only. Not done: #1-20, #34-35.

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Strong preference for \\ M2 over M1\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M4. D/P+A/B asym}     & \textbf{-1223.28}                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors of  ploidy only models without diplodization. Results indicate that a character independent model (M2) is strongly preferred over BiSSE (M1)  model. There is no evidence that character independent model is different from M4, the HiSSE model with asymmetric hidden rates. M4 is moderately preferred over the more complicated M5, a HiSSE model that has asymmetry for all transition rates.}
\label{table:M1M5}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                           & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M7    & M8     & M9    & M10   & Evidence                                                                                     \\ \hline
M6. D/P+$\delta$                & -1268.83                                                          & 55.41 & 42.78  & 53.37 & 52.85 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M6\end{tabular}            \\ \hline
\textbf{M7. CID D/P+$\delta$}   & \textbf{-1212.42}                                                 &       & -12.62 & -2.04 & -2.04 & \begin{tabular}[c]{@{}l@{}}Model M7 moderately\\ preferred over M9 and M10\end{tabular}      \\ \hline
M8. D/P+A/B $\delta$            & -1214.46                                                          &       &        & 10.58 & 10.07 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular} \\ \hline
M9. D/P+A/B +$\delta$ asym      & -1214.46                                                          &       &        &       & -0.51 & No evidence                                                                                  \\ \hline
M10. D/P+A/B +$\delta$ all asym & -1214.97                                                          &       &        &       &       &         \\ \hline                                                                                    
\end{tabular}
\caption{Bayes factors of  ploidy only models with diplodization. Results indicate that a character independent model (M6) is strongly preferred over BiSSE (M1)  model. M6 is moderately preferred over any of the HiSSE models with asymmetric hidden rates (M9, M10).}
\label{table:M6M10}
\end{table}

% M111 -> M11
\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.34 & 61.40 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M11\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.21 & 20.37 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.75 & 22.80 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.72}                                                 &       &       &       & 0.05 & No evidence                                                                                    \\ \hline
\textbf{M15. I/C+A/B all asym }     & \textbf{ -1247.66}                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors of breeding system only models. Results indicate that the HiSSE models with asymmetric rates (M14, M15) are strongly preferred over every other model.}
\label{table:M11M15}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                            & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M18   & M19   & M20   & Evidence                                                                                                   \\ \hline
M16. ID/CP/CD                    & -1459.11                                                          & 45.11 & 65.91 & 63.98 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M16\end{tabular}                         \\ \hline
M17. CID ID/CP/CD                & *                                                                 &       &       &       &                                                                                                            \\
M18. ID/CP/CD+A/B                & -1414                                                             &       & 20.79 & 18.87 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}               \\ \hline
\textbf{M19. ID/CP/CD +A/B asym} & \textbf{-1393.20}                                                 &       &       & -1.92 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates moderately\\ preferred over all asymmetric\end{tabular} \\ \hline
M20. ID/CP/CD +A/B all asym      & -1393.12                                                          &       &       &       &   \\ \hline                                                                                                        
\end{tabular}
\caption{Bayes factors of ploidy and breeding system withou diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (17) is  strongly preferred over M16 and M18 and moderately preferred over the MuHiSSe with all rates asymetric (M20). *Marginal log-likelihood for M17 could not be calculated in our limited amount of computational time.}
\end{table}

>>>>

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Strong preference for \\ M2 over M1\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M4. D/P+A/B asym}     & \textbf{-1223.28}                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors for ploidy-only models without diplodization. Results indicate that a character independent model (M2) is strongly preferred over BiSSE (M1)  model. There is no evidence that character independent model is different from M4, the HiSSE model with asymmetric hidden rates. M4 is moderately preferred over the more complicated M5, a HiSSE model that has asymmetry for all transition rates.}
\label{table:M1M5}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                           & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M7    & M8     & M9    & M10   & Evidence                                                                                     \\ \hline
M6. D/P+$\delta$                & -1268.83                                                          & 55.41 & 42.78  & 53.37 & 52.85 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M6\end{tabular}            \\ \hline
\textbf{M7. CID D/P+$\delta$}   & \textbf{-1212.42}                                                 &       & -12.62 & -2.04 & -2.04 & \begin{tabular}[c]{@{}l@{}}Model M7 moderately\\ preferred over M9 and M10\end{tabular}      \\ \hline
M8. D/P+A/B $\delta$            & -1214.46                                                          &       &        & 10.58 & 10.07 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular} \\ \hline
M9. D/P+A/B +$\delta$ asym      & -1214.46                                                          &       &        &       & -0.51 & No evidence                                                                                  \\ \hline
M10. D/P+A/B +$\delta$ all asym & -1214.97                                                          &       &        &       &       &         \\ \hline                                                                                    
\end{tabular}
\caption{Bayes factors for ploidy-only models with diplodization. 
Results indicate that a character-independent model (M6) is strongly preferred over BiSSE (M1) model. 
M6 is moderately preferred over any of the HiSSE models with asymmetric hidden rates (M9, M10).}
\label{table:M6M10}
\end{table}

% M111 -> M11
\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.34 & 61.40 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M11\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.21 & 20.37 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.75 & 22.80 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.72}                                                 &       &       &       & 0.05 & No evidence                                                                                    \\ \hline
\textbf{M15. I/C+A/B all asym }     & \textbf{ -1247.66}                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors for breeding system-only models. 
Results indicate that the HiSSE models with asymmetric rates (M14, M15) are strongly preferred over other models.}
\label{table:M11M15}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                            & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M18   & M19   & M20   & Evidence                                                                                                   \\ \hline
M16. ID/CP/CD                    & -1459.11                                                          & 45.11 & 65.91 & 63.98 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M16\end{tabular}                         \\ \hline
M17. CID ID/CP/CD                & *                                                                 &       &       &       &                                                                                                            \\
M18. ID/CP/CD+A/B                & -1414                                                             &       & 20.79 & 18.87 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}               \\ \hline
\textbf{M19. ID/CP/CD +A/B asym} & \textbf{-1393.20}                                                 &       &       & -1.92 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates moderately\\ preferred over all asymmetric\end{tabular} \\ \hline
M20. ID/CP/CD +A/B all asym      & -1393.12                                                          &       &       &       &   \\ \hline                                                                                                        
\end{tabular}
\caption{Bayes factors of ploidy and breeding system without diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (17) is  strongly preferred over M16 and M18 and moderately preferred over the MuHiSSe with all rates asymetric (M20). *Marginal log-likelihood for M17 could not be calculated in our limited amount of computational time.}
\end{table}
